\section{Project Organization}
\subsection{Responsibilities \& Roles}
\begin{comment}
    Erik communications
    Simon møtereferattaker
    Eller har vi samme responsabilities & roles, 
\end{comment}

\subsection{Routines \& Group Rules}
% General
% Sickness
% Communication
% Meetings
\subsubsection{General}
\begin{itemize}
    \item The members of the group should work a minimum of 30 hours together per week, preferably on campus.
    \item Decisions that impact the final product should be discussed with the other group member.
    \item All work hours must be recorded with Traggo.
    % TODO: Traggo / Toggl?^
\end{itemize}

\subsubsection{Sickness}
\begin{itemize}
    \item If a group member is sick or for other reasons cannot work, it is still expected that they do their best to get some work done.
    \item If necessary, the other group member is expected to cover for the sick member to ensure a consistent workload.
\end{itemize}

\subsubsection{Meetings}
\begin{itemize}
    \item Meetings with the supervisor will be held every Tuesday at 12:00, unless not necessary or the time is not suitable.
    \item Sprint meetings will be held every Monday, while also having daily scrum meetings.
    \item The proceedings of each meeting will be documented.
\end{itemize}

\subsubsection{Communication}
\begin{itemize}
    \item Mutual respect, civility, and humility are required by the group members.
    \item Disagreements are welcome as they are a natural part of working in a team and are vital to any nuanced discussion.
\end{itemize}